### 2011-05-23 tags/crisp-1.1.6/trunk/Papers/reasoning-challenges/introduction.tex
[maven-release-plugin]  copy for tag crisp-1.1.6

The International Planning Competition (IPC)\footnote{See
\url{http://ipc.icaps-conference.org/}.} recently celebrated its 10-year
anniversary in 2008. During this time, six instances of the IPC have been
run, each of which has helped drive the development of new planning
technology, by providing a regular forum for showcasing the latest trends
in planner design, domain description languages, and challenging planning
domains. Given the absence of a competition in 2010---breaking the
competition's established two year cycle for the first time since its
inception---we feel the time is right to revisit the structure of the
existing IPC, and suggest a new direction for the competition in the
future.

>>>>

The International Planning Competition (IPC)\footnote{See
\url{http://ipc.icaps-conference.org/}.} recently celebrated its 10-year
anniversary in 2008. During this time, six instances of the IPC have been
run, each of which has helped drive the development of new planning
technology by providing a regular forum for showcasing the latest trends
in planner design, domain description languages, and challenging planning
domains. Given the absence of a competition in 2010---breaking the
competition's established two year cycle for the first time since its
inception---we feel the time is right to revisit the structure of the
existing IPC, and suggest a new direction for the competition in the
future.

### 2011-05-23 tags/crisp-1.1.6/trunk/Papers/reasoning-challenges/levels.tex
[maven-release-plugin]  copy for tag crisp-1.1.6

While this format for the IPC has been highly successful in the past
ten years, there is also a number of ways in which it can be improved
and streamlined.  One such direction concerns the way in which problem
classes are collected.  There is no doubt that the existing collection
of IPC domains is a fundamental driving force for the development of
new planning algorithms.  Unfortunately, the current selection process
makes it difficult for users of these systems, who may come from
different communities, to get a new application-motivated domain
accepted as an IPC benchmark.  This is unsurprising, given that IPC
organizers must be able to justify their selection of domains, and
picking untested domains from other communities is not the best way to
do this.  However, this leads to a selection process that is less
dynamic than it could be, and more restrictive for users wanting to
contribute suggestions.  Conversely, to keep the number of domains
that must be tested in each round of the competition manageable, older
domains are sometimes ``retired'', i.e.\ removed from subsequent
competitions.  This comes with a risk of a false sense of progress, in
which retired domains are remembered as ``solved'' although they were
removed for completely independent reasons.  Finally, it has been
argued \cite{ToughNuts} that IPC organizers may be tempted to favor
the development of new types of planning problems and new dialects of
PDDL over trying to find challenging benchmark problems for existing
versions of PDDL. Such approaches run the risk of ``reinventing'' past
problem classes (albeit in different guises), or redirecting
investigation away from current challenges.

@@

Problem classes and instances can be submitted by any registered user. 
Submitting a problem class should involve three pieces of data. First,
the user should submit a collection of instances of the problem class or
a generator for such instances.  Second, the user should specify some
metadata including the class name and a human-readable description,
possibly with links to the applicable literature, complexity results, and
so on.  Third, the user should specify the \emph{type} of problem class,
which determines what systems the data is suitable for, i.e., the language
in which the problem is specified (such as a particular dialect of PDDL or
EUROPA \todo{cite}) and the type of planning problem (e.g., propositional,
temporal, uncertainty, etc.).  If it is possible to convert between one
specification language and another automatically, this conversion could be
performed each time a problem is submitted.
In order to avoid abuse, the number of instances should be limited (e.g.,
per hour), and a simple validity check should be possible (e.g., running a
parser to verify that the format is PDDL).

@@

Of course, several issues need to be addressed to make this possible.
The first is how we can allow users to upload their systems and still
expect to run and maybe compile them automatically, without requiring
the manual intervention of an organizer if things break.  This problem
can be solved by imposing strict requirements on the execution
environment of the planner.  One way in which we could envision this
is by defining a single hardware and software environment in which
systems will be evaluated, and making it available for download as a
virtual machine image.  Developers can then run this image on their
own machine, using a virtual machine such as
VirtualBox,\footnote{\url{http://www.virtualbox.org/}} and ensure
that their system works, in the exact environment in which it will be
evaluated.  This would even make it technically possible for
participants to submit not the source code, but a binary executable
(perhaps along with support files).  However, even if we require the
submission of source code, the move to a precisely defined environment
that contains only standard versions of tools and libraries and on
which the code must compile without human intervention enforces at
least a certain degree of portability from which users will benefit
when they download the systems.  Even when the environment changes to
reflect updates in the standard development environments (new version
of the C compiler, etc.), old images could remain available, and so
old systems would continue running until the virtual machine emulator
itself becomes unavailable or incompatible.

We propose that every newly submitted system is run automatically on
all available problem instances, and every newly submitted problem
instance is sent to all available systems.  The scheduling of this
process can be under the control of an automated system for continuous
integration, such as Hudson.\footnote{\url{http://hudson-ci.org/}} The
evaluation infrastructure sends the problem data and the system to the
test machine, runs the system, measures performance statistics
(including which problems they could solve and how much time this took
them; see below), and stores the results in a database. Users will be
able to view the results in dynamically generated reports on the main
website; there may also be functionality to customize these reports to
focus on certain types of problems.  Because all systems are run on
all problem instances, and users can ensure that challenging problem
instances are included in the competition, the chance of systems being
evaluated on only a small and somewhat arbitrary selection of problem
instances \cite{pg2008002} can be avoided.

In order to minimize security risks, which can arise when
user-submitted programs are being run automatically, the test machines
need to be sandboxed quite tightly.  In particular, the machines do
not need to be able to initiate any network connections, beyond being
able to enter performance measurements into a database, and can work
on virtual file systems that are deleted after each system.  By
further imposing resource limits on the number of available
processors, memory and processor time, and disk space, we believe the
potential for abuse is limited.  It can be limited further by only
allowing systems uploads to registered users.

While we see our proposed system's ability to generate up-to-date
reports automatically as a major strength, there may still be a
benefit in maintaining the current style of regular competitions at
discrete timepoints, e.g., to encourage the development of faster
systems through awards.  Such a competition could easily be based on
our system, by announcing a deadline and a specified subset of problem
classes. The selection of this subset could be informed, among other
things, by the report on problems that many systems can't
solve. Participants could then upload their systems at their leisure;
``running'' the competition amounts to taking a snapshot of the
performance reports on the selected problems when the deadline comes
and announcing the results.  By recording timestamps whenever a
performance measurements is made, this snapshot could remain available
on the website simply as one special report for a certain point in
time.  In such a case, the authors of systems should have the option
of marking them as ``non-competing'' to exclude them from the
competition snapshot, and maybe also from the up-to-date performance
reports.

@@

The continuous evaluation infrastructure we just presented is
fundamentally agnostic to the type of concrete evaluation measures
that it collects.  In particular, traditional measures such as the
percentage of problems solved per system, average solution quality,
average runtime and memory use, and search tree sizes can be collected
-- with the caveat that the test machines must be configured so as to
allow comparable runtime measurements.  Furthermore, popularity scores
from the social networking aspect can be incorporated, or different
measures could be combined into an overall score.

@@

One advantage of the evaluation infrastructure proposed above is that
its applicability is not limited to the evaluation of planners.
%RP: I don't see why this needs to be restricted to "reasoning" tasks
Many reasoning tasks, including constraint solving and theorem
proving, are being evaluated by running solvers over problem instances
and reporting performance measures.  At the level of abstraction at
which our continuous evaluation system could be implemented, there is
no fundamental difference between the problem type ``deterministic
planning problem in PDDL 1.0'' and the problem type ``theorem of
first-order logic in TPTP format'' -- in both cases, the system can
collect problem classes and instances of this type and run them
through solvers that declare themselves to accept such inputs.  In
fact, other fields are already ahead of the planning community in
maintaining problem repositories as on Level 1 above
\cite{SS98,csplib,Asuncion+Newman:2007}. This means that there is a
potential for sharing development and maintenance costs for the
evaluation platform among different communities.

>>>>

While this format for the IPC has been highly successful in the past
ten years, there are also a number of ways in which it can be improved
and streamlined.  One such direction concerns the way in which problem
classes are collected.  There is no doubt that the existing collection
of IPC domains is a fundamental driving force for the development of
new planning algorithms.  Unfortunately, the current selection process
makes it difficult for users of these systems, who may come from
different communities, to get a new application-motivated domain
accepted as an IPC benchmark.  This is unsurprising, given that IPC
organizers must be able to justify their selection of domains, and
picking untested domains from other communities is not the best way to
do this.  However, this leads to a selection process that is less
dynamic than it could be, and more restrictive for users wanting to
contribute suggestions.  Conversely, to keep the number of domains
that must be tested in each round of the competition manageable, older
domains are sometimes ``retired'', i.e., removed from subsequent
competitions.  This comes with a risk of a false sense of progress, in
which retired domains are remembered as ``solved'' although they were
removed for completely independent reasons.  Finally, it has been
argued \cite{ToughNuts} that IPC organizers may be tempted to favor
the development of new types of planning problems and new dialects of
PDDL over trying to find challenging benchmark problems for existing
versions of PDDL. Such approaches run the risk of ``reinventing'' past
problem classes (albeit in different guises), or redirecting
investigation away from current challenges.

@@

Problem classes and instances can be submitted by any registered user. 
Submitting a problem class should involve three pieces of data. First,
the user should submit a collection of instances of the problem class or
a generator for such instances.  Second, the user should specify some
metadata including the class name and a human-readable description,
possibly with links to the applicable literature, complexity results, and
so on.  Third, the user should specify the \emph{type} of problem class,
which determines what systems the data is suitable for, i.e., the language
in which the problem is specified (such as a particular dialect of PDDL)
and the type of planning problem (e.g., propositional,
temporal, uncertainty).  If it is possible to convert between one
specification language and another automatically, this conversion could be
performed each time a problem is submitted.
In order to avoid abuse, the number of instances should be limited (e.g.,
per hour), and a simple validity check should be possible (e.g., running a
parser to verify that the format is PDDL).

@@

Of course, several issues need to be addressed to make this possible.
The first is how we can allow users to upload their systems and still
expect to run and maybe compile them automatically, without requiring
the manual intervention of an organizer if things break.  This problem
can be solved by imposing strict requirements on the execution
environment of the planner.  One way in which we could envision this
is by defining a single hardware and software environment in which
systems will be evaluated, and making it available for download as a
virtual machine image.  Developers can then run this image on their
own machine, using a virtual machine such as
VirtualBox,\footnote{\url{http://www.virtualbox.org/}} and ensure
that their system works in the exact environment in which it will be
evaluated.  This would even make it technically possible for
participants to submit not the source code, but a binary executable
(perhaps along with support files).  However, even if we require the
submission of source code, the move to a precisely defined environment
that contains only standard versions of tools and libraries and on
which the code must compile without human intervention enforces at
least a certain degree of portability from which users will benefit
when they download the systems.  Even when the environment changes to
reflect updates in the standard development environments (e.g., a new version
of the C compiler), old images could remain available, and so
old systems would continue running until the virtual machine emulator
itself becomes unavailable or incompatible.

We propose that every newly submitted system be run automatically on
all available problem instances, and every newly submitted problem
instance be sent to all available systems.  The scheduling of this
process can be under the control of an automated system for continuous
integration, such as Hudson.\footnote{\url{http://hudson-ci.org/}} The
evaluation infrastructure would send the problem data and the system to the
test machine, run the system, measure performance statistics
(including which problems they could solve and how much time this took
them; see below), and store the results in a database. Users would be
able to view the results in dynamically generated reports on the main
website; there may also be functionality to customize these reports to
focus on certain types of problems.  Because all systems are run on
all problem instances, and users can ensure that challenging problem
instances are included in the competition, the chance of systems being
evaluated on only a small and somewhat arbitrary selection of problem
instances \cite{pg2008002} can be avoided.

In order to minimize security risks, which can arise when
user-submitted programs are run automatically, the test machines
need to be sandboxed quite tightly.  In particular, the machines do
not need to be able to initiate any network connections, beyond being
able to enter performance measurements into a database, and can work
on virtual file systems that are deleted after each execution.  By
further imposing resource limits on the number of available
processors, memory and processor time, and disk space, we believe the
potential for abuse is limited.  It can be limited further by only
allowing system uploads to registered users.

While we see our proposed system's ability to generate up-to-date
reports automatically as a major strength, there may still be a
benefit in maintaining the current style of regular competitions at
discrete timepoints, e.g., to encourage the development of faster
systems through awards.  Such a competition could easily be based on
our system, by announcing a deadline and a specified subset of problem
classes. The selection of this subset could be informed, among other
things, by the report on problems that many systems had difficulty
solving. Participants could then upload their systems at their leisure;
``running'' the competition would amount to taking a snapshot of the
performance reports on the selected problems when the deadline comes
and announcing the results.  By recording timestamps whenever a
performance measurement is made, this snapshot could remain available
on the website simply as one special report for a certain point in
time.  In such a case, the authors of systems should have the option
of marking them as ``non-competing'' to exclude them from the
competition snapshot, and maybe also from the up-to-date performance
reports.

@@

The continuous evaluation infrastructure we have presented is
fundamentally agnostic to the type of concrete evaluation measures
that it collects.  In particular, traditional measures such as the
percentage of problems solved per system, average solution quality,
average runtime and memory use, and search tree sizes can be collected
-- with the caveat that the test machines must be configured so as to
allow comparable runtime measurements.  Furthermore, popularity scores
from the social networking aspect can be incorporated, or different
measures could be combined into an overall score.

@@

One advantage of the evaluation infrastructure proposed above is that
its applicability is not limited to the evaluation of planners.
%RP: I don't see why this needs to be restricted to "reasoning" tasks
Many reasoning tasks, including constraint solving and theorem
proving, are evaluated by running solvers over problem instances
and reporting performance measures.  At the level of abstraction at
which our continuous evaluation system could be implemented, there is
no fundamental difference between the problem type ``deterministic
planning problem in PDDL 1.0'' and the problem type ``theorem of
first-order logic in TPTP format'' -- in both cases, the system can
collect problem classes and instances of this type and run them
through solvers that declare themselves to accept such inputs.  In
fact, other fields are already ahead of the planning community in
maintaining problem repositories as on Level 1 above
\cite{SS98,csplib,Asuncion+Newman:2007}. This means that there is a
potential for sharing development and maintenance costs for the
evaluation platform among different communities.
